---
title: "Practical"
format: html
editor: source
---

## Introduction

The `bvarnet` package implements methods to analyse (multilevel) Vector Autoregression commonly used for the analysis of intensive longitudinal datasets like EMA data.

## Data

Load the example dataset using
```{r}
data(studentlife)
```

Now inspect the data 
```{r}

```

What outcome model would you choose for this dataset?

## Prior Specification

First we need to specify the prior distributions that we want to use on the parameters.
For this we can use the `set_priors()` function. As we are running a ordinal model, without covariates, we have to specify priors on the temporal structure (denoted by the $\Phi$ matrix) and on the category threshold parameters ($\kappa$) which is specific to the adjacent category ordinal model.

You can choose priors using the following function. For now, we want to specify uninformative normal priors. Pick location and scale values for uninformative prior specification:
```{r}
priors <- set_priors(phi = prior(family = "normal",
                                 loc = _,
                                 scale = _),
                     kappa = prior(family = "normal",
                                   loc = _,
                                   scale = _))

priors
```

Currently, three prior families are implemented: normal, student-t and chauchy. For standart deviations and random effects all of these priors are automatically scaled to half-priors. 
For each distribution, the location and scale parameters can be specified. For the student-t distribution, the degrees of freedom can also be specified. 

## Model Estimation

We want to estimate a temporal network for the variables `anxious`, `calm`, `conventional`, `critical`, `dependable`. Additionally, we want to control for the covariate `sleep_hour`. Use `?bvar` to learn about the fit function syntax.
We also want to estimate a random intercept and person-specific random slopes for the lagged coefficients. You can do this using `re_cols = c("Intercept")` and `re_temporal = TRUE`.

```{r}

```

## Inspect the results

You can inspect the results using the `summary()` function.
If the output ios too large to be displayed, you can use the `extract_param()` function to extract a data frame with all estimated parameters.

```{r}

```

## Hypothesis Testing using Bayes Factors

To estimate Bayes factors for a single parameter, or a set of parameters, we can use the `bf_table()` function. Bayes factors are computed via the **Savage–Dickey density ratio** (SDDR), which, for a point null $H_0 : \theta = \theta_0$ nested in $H_1 : \theta \neq \theta_0$ with shared nuisance parameters, gives

$$
\mathrm{BF}_{01} \;=\; \frac{p(\theta = \theta_0 \mid y)}{p(\theta = \theta_0)},
$$

i.e. the ratio of the posterior to the prior density evaluated at the null value. `bf_table()` reports $\mathrm{BF}_{10} = 1 / \mathrm{BF}_{01}$ by approximating the posterior density at $\theta_0 = 0$ from the MCMC draws.

To perform a hypothesis test on effects involving a specific variable, we can call the `bf_table()` function, specifying which variable we want to look at using the `variable` argument. Lets investigate if the hours of sleep the individual got in the previous night (`sleep_hour`) has an influence on the network structure:

```{r}
bf_tab <- bf_table(fit, variable = "sleep_hour")
bf_tab
```

The output now shows 6 rows. The five "Fixed Effect" rows show if the the covariate `sleep_hour` has an influence on each node separately. The "Fixed Effect (join)" row displays a single Bayes factor that in this case tests the hypothesis

H: Is there a difference in the baseline of the network structure that is explained by the variable `sleep_hour`

Interpret the Bayes factor:

## Plot the network

Using the `qgraph` package and the `extract_network_matrix()` function you can easily plot the estimated network
```{r}
nw_mat <- extract_network_matrix(fit)
qgraph(nw_mat)
```

